### 2012-10-25 paper_draft.tex
Added acknowledgment to openSNP's users

% Title must be 150 characters or less
\begin{flushleft}
{\Large
\textbf{openSNP - Crowdsourcing Genome-Wide Association Studies}
}
% Alternative titles: 
% openSNP - a new, open data-source for personalised medicine
% What kind of person would share genotyping-data? Presenting a survey and an open data-source for personalised medicine
% 
% Insert Author names, affiliations and corresponding author email.
\\
Bastian Greshake$^{1,\ast}$, 
Philipp Bayer$^{2}$, 
Fabian Zimmer$^{3}$,
Julia Reda$^{4}$
\\
\bf{1} Goethe University, Frankfurt am Main, Germany
\\
\bf{2} University of Queensland, Brisbane, Australia
\\
\bf{3} Westf\"alische Wilhelms Universit\"at, M\"unster, Germany
\\
\bf{4} Johannes-Gutenberg University, Mainz, Germany
\\
$\ast$ E-mail: info@opensnp.org
\end{flushleft}

@@

A flowchart of all services incorporated in openSNP and of all the ways users can upload or access the data is given in figure \ref{Figure4_label}. The source code of openSNP is 
published under the MIT-license and can be downloaded at http://github.com/gedankenstuecke/snpr. The genetical and phenotypical data is licensed under Creative Commons Zero. 
% Do NOT remove this, even if you are not including acknowledgments
\section*{Acknowledgments}
We thank Dr. Manuel Corpas for constructive advice in grammar, spelling and structure of this study.

>>>>

% Title must be 150 characters or less
\begin{flushleft}
{\Large
\textbf{openSNP - Crowdsourcing Genome-Wide Association Studies}
}
% Alternative titles: 
% openSNP - a new, open data-source for personalised medicine
% What kind of person would share genotyping-data? Presenting a survey and an open data-source for personalised medicine
% 
% Insert Author names, affiliations and corresponding author email.
\\
Bastian Greshake$^{1,\ast}$, 
Philipp Bayer$^{2}$, 
Fabian Zimmer$^{3}$,
Julia Reda$^{4}$,
Helge Rausch$^{5}$
\\
\bf{1} Goethe University, Frankfurt am Main, Germany
\\
\bf{2} University of Queensland, Brisbane, Australia
\\
\bf{3} Westf\"alische Wilhelms Universit\"at, M\"unster, Germany
\\
\bf{4} Johannes-Gutenberg University, Mainz, Germany
\\
\bf{5} Hochschule für Technik und Wirtschaft, Berlin, Germany
\\
$\ast$ E-mail: info@opensnp.org
\end{flushleft}

@@

A flowchart of all services incorporated in openSNP and of all the ways users can upload or access the data is given in figure \ref{Figure4_label}. The source code of openSNP is 
published under the MIT-license and can be downloaded at http://github.com/gedankenstuecke/snpr. The genetical and phenotypical data is licensed under Creative Commons Zero. 
% Do NOT remove this, even if you are not including acknowledgments
\section*{Acknowledgments}
We thank Dr. Manuel Corpas and Prof. Dr. Dave Edwards for constructive advice in grammar, spelling and structure of this study. We would also like to thank the users of openSNP.org for their participation, their constructive criticisms and bug-finding abilities and especially for sharing their genotyping and phenotype data.
